Analysis

### 2019-08-17 reports/manuscript.Rmd
finish introduction of experiment 2

We tested the memory performance in an paradigm inspired by Deese-Roedrigez-McDermott paradigm [DRM, @Deese1959, @Roediger1995]. We presented the scenes and participants task was to memorize then. The similairty defined by image space serves as valid tool how to quantify similarity of stimuli and describe the presented stimuli using the coordinates in image space, where the center of presented stimuli should lie. we queried teh subjects with either seen or unseen scenes, while we varied, whether the scenes were closer to the center of the presented scenes or further away. If the visual stimuli are internally represented in a structure showing resemblance to the image space, there should be more false alarms for the distractors closer to the center than for distractors further away from the

>>>>

We tested the memory performance in an paradigm inspired by Deese-Roedrigez-McDermott paradigm [DRM, @Deese1959, @Roediger1995]. We presented the scenes and participants task was to memorize then. The similairty defined by image space serves as valid tool how to quantify similarity of stimuli and describe the presented stimuli using the coordinates in image space, where the center of presented stimuli should lie. we queried teh subjects with either seen or unseen scenes, while we varied, whether the scenes were closer to the center of the presented scenes or further away. If the visual stimuli are internally represented in a structure showing resemblance to the image space, there should be more false alarms for the distractors closer to the center than for distractors further away from the center, as the center represent the visual prototype [@Posner1969].
